Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-20 paper/main.tex
paper updates

@@

>>>>

\subsection{Label}

The label we would ideally like to use would be whether or not a term is the
true source of the crash; that is, whether the correct way to fix the crash is
to edit this term. However, manually labeling terms in such a way would be
prohibitive on such a large dataset. And the whole point of this work is that
there does not yet exist a reliable way of pinpointing bugs automatically. Thus
we are forced to use a proxy for our desired label as follows. Many PythonTutor
users use the site in an iterative fashion: they start out by writing
a program that crashes, and then edit it until it no longer crashes. Thus for our
dataset, we consider only the crashing programs for which the same user later
ran a program that did not crash. We then run a tree-diff \cite{tree-diff}
between the program that crashes and the one that does not. Any terms in the
crashing program that appear in the diff are labeled as bugs. This is of course
not a perfect proxy for the label we want; see Threats to Validity.

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={Top-1,Top-3},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=All, col sep=comma]{defect-categories.csv};
    \addplot table[x=scoreName, y=TypeError, col sep=comma]{defect-categories.csv};
    \addplot table[x=scoreName, y=AttributeError, col sep=comma]{defect-categories.csv};
\legend{All Errors,TypeError,AttributeError}
\end{axis}
\end{tikzpicture}
\caption{Accuracy when using only a subset of the data that all has the same crash. TODO:
get separate baselines?}
\label{fig:defect-categories}
\end{figure}
